---
title: "MATH 189 Homework 3"
author: "Weixiu Dong, Mengheng Yang, Xuqian Tan, Yushan Liu, Iris Ziyi Wang"
date: "1/20/2020"
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset Description
```{r}
data <- read.csv('AB_NYC_2019.csv')
```

This dataset describes the Airbnb listing activity and metrics in NYC, NY for 2019.
There are 48896 observations.
 
Reference: 

```{r}
names(data)
dim(data)
head(data)
```
There are 16 variables (with explanations):
1. Id (listing ID), 
2. name (name of the listing), 
3. host_id (host ID), 
4. host_name (name of the host) 
5. neighbourhood_group (location), 
6. neighbourhood (area), 
7. latitude (latitude coordinates), 
8. longitude (longitude coordinates), 
9. room_type (listing space type), 
10. price (price in dollars), 
11. minimum_nights (amount of nights minimum), 
12. number_of_reviews (number of reviews), 
13. last_review (latest review), 
14. reviews_per_month (number of reviews per month), 
15. calculated_host_listings_count (amount of listing per host), 
16. availability_365 (number of days when listing is available for booking)

## Research Question
How does room types affect the traffic (number of listings) among different areas?

## Data Cleaning
```{r}
keeps <- c('neighbourhood_group', 'room_type','price','minimum_nights', 'number_of_reviews','avalibility_365')
df = data[,names(data) %in% keeps]
names(df)
dim(df)
head(df)
```

## Table one
There are 3 different categories for room type: **Private room**, **Entire home/apt** and  **Shared room**.    
```{r}
summary(as.factor(data$room_type))
```

Let's first sepearate the categorical vs. discrete variables. 
Then, keep only relevant columns in our production of table one.
```{r}
colnames(data)
```

```{r}
# var to display in table
myVars <- c("neighbourhood_group" , "latitude", "longitude", "price", "minimum_nights", "number_of_reviews", "reviews_per_month", "calculated_host_listings_count","availability_365")
    
# categorical
catVars <- c("neighbourhood_group")# , "neighbourhood")

# continous
contVars <- c("latitude", "longitude", "price", "minimum_nights", "number_of_reviews", "reviews_per_month", "calculated_host_listings_count","availability_365")


```

Now let's make Table 1 for this dataset.
```{r}
library(tableone)
tbl <- CreateTableOne(vars = myVars, strata = "room_type" , data = data)#, factorVars = catVars)

tbl
```

## Including Plots

### Bar plots for categorical variables

```{r, echo=FALSE}
library(ggplot2)
bar_tbl <- with(data, table(room_type, neighbourhood_group ))

ggplot(as.data.frame(bar_tbl), aes(x= factor(room_type), y = Freq , fill =neighbourhood_group)) +
  geom_bar(stat="identity", position = "dodge") + 
  scale_fill_brewer(palette = "Set1")
```

### Plots for continous variable

We first use boxplots to explore **latitude** and **longtitude**

```{r}
ggplot(data, aes(x=room_type, y= latitude)) + 
    geom_boxplot()
```


```{r}
ggplot(data, aes(x=room_type, y= longitude)) + 
    geom_boxplot()
```

and also **availability_365**.
```{r}
ggplot(data, aes(x=room_type, y= availability_365)) + 
    geom_boxplot()
```


Then, we explore some variables that are highly skewed with both boxplots and histgorams by groups.

Let's first take a look at **price** by groups.
```{r}
ggplot(data,aes(x=price))+
    geom_histogram(bins = 100)+
    facet_grid(~room_type)+
    theme_bw()

ggplot(data, aes(x=room_type, y=price)) + 
    geom_boxplot()

```

Then **minimum_nights**. 
```{r}

ggplot(data,aes(x=minimum_nights))+
    geom_histogram(bins = 100)+
    facet_grid(~room_type)+
    theme_bw()

ggplot(data, aes(x=room_type, y= minimum_nights)) + 
    geom_boxplot()

```

We can also look into **reviews per month**, with na values removed. 
```{r}
ggplot(data, aes(x=room_type, y= reviews_per_month,na.rm = TRUE)) + 
    geom_boxplot(na.rm = TRUE)


ggplot(data,aes(x=reviews_per_month,na.rm = TRUE))+
    geom_histogram(na.rm = TRUE, bins = 100)+
    facet_grid(~room_type)+
    theme_bw()
```

Last but not the least, the **calculated_host_listings_count**.

```{r}

ggplot(data, aes(x=room_type, y= calculated_host_listings_count,na.rm = TRUE)) + 
    geom_boxplot(na.rm = TRUE)


ggplot(data,aes(x=calculated_host_listings_count))+
    geom_histogram( bins = 100)+
    facet_grid(~room_type)+
    theme_bw()
```


We can look into **number_of_review** by just investigating the histogram by groups.
```{r}
ggplot(data,aes(x=number_of_reviews))+
    geom_histogram(bins = 100)+
    facet_grid(~room_type)+
    theme_bw()
```
